Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-19 paper/v2.0/sections/appendix_d.tex
Correct appD

In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system. We already found the exact solution for our time-dependent Hamiltonian give in Eq.~(\ref{eq_1}) and we identified them as the Floquet states in Eq.~(\ref{eq_12}). The Floquet modes derived in Eq.~(\ref{eq_9}) can be represented as quantum states using their corresponding quantum numbers for the simplicity of notation as follows
\begin{equation} \label{eq_d1}
  \ket{\phi_{n,m}} = \ket{n,k_x}.
\end{equation}
Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
\begin{equation} \label{eq_d2}
  \qty(\vb{j})_{nm,n'm'} \equiv \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
\end{equation}
Thus, the particle current operator for our system \cite{mahan00,bruus04} can be identified as
\begin{equation} \label{eq_d3}
  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]),
\end{equation}
where $\widetilde{m}$ is the mass of the considering particle.

First, we consider the $x$-directional current operator component, and we can identify that the $x$-directional current operator as
\begin{equation} \label{eq_d4}
  \hat{j}_x = \frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{x} + eBy).
\end{equation}
Next, we calculate the matrix elements of $x$-directional current operator in Floquet mode basis
\begin{equation} \label{eq_d5}
  \qty({j}_x)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x},
\end{equation}
and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq_7}) as follows
\begin{equation} \label{eq_d6}
  \begin{aligned}
    \qty({j}_x)_{nm,n'm'} = &
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int dy \;
    \Big[
    \qty[\hbar k'_x + eBy] \\
    & \times
     \chi_{n}\big(y - y_0 - \zeta(t)\big)
    \chi_{n'}\big(y - y_0 - \zeta(t)\big)
    \Big].
  \end{aligned}
\end{equation}
Let $(y - y_0 - \zeta(t)) = \bar{y}$ and we can obtain
\begin{equation} \label{eq_d7}
  \begin{aligned}
    \qty({j}_x)_{nm,n'm'} =
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int d\bar{y} \;
    \Big[ &
    \qty[\hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)] \\
    & \times
    \chi_{n}(\bar{y})
    \chi_{n'}(\bar{y})
    \Big].
  \end{aligned}
\end{equation}
Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
\begin{subequations} \label{eq_d8}
  \begin{align}
    \int d{y} \;
    \chi_{n}({y})
    \chi_{n'}({y}) &=
    \delta_{n',n}, \\
    \int dy \;
    y
    \chi_{n}({y})
    \chi_{n'}({y}) &=
    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}),
  \end{align}
\end{subequations}
we simplify the matrix elements of $x$-directional current operator to obtain
\begin{equation} \label{eq_d9}
  \begin{aligned}
    \qty({j}_x)&_{nm,n'm'} =
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    eB\\
    & \times
    \bigg[
    \bigg(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}\bigg)
    + \zeta(t) \delta_{n',n}
    \bigg].
  \end{aligned}
\end{equation}
Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we identify the $0$-th component of the Fourier series as
\begin{equation} \label{eq_d10}
  \begin{aligned}
      \qty({j}^x_{s=0})_{nm,n'm'} =&
      \frac{eB}{{\widetilde{m}}}
      \delta_{k_x,k'_x} \\
      & \times
      \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1}).
  \end{aligned}
\end{equation}
For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
\begin{equation} \label{eq_d11}
  \begin{aligned}
      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron} =&
      \frac{e^2B}{{m_e}}
      \delta_{k_x,k'_x}\\
      & \times
      \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1}).
  \end{aligned}
\end{equation}

Moreover, we can identify the $y$-directional current operator component as
\begin{equation} \label{eq_d12}
  \hat{j}_y = \frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
\end{equation}
Using this operator, the matrix elements of $y$-directional current operator in Floquet mode basis can be represented as
\begin{equation} \label{eq_d13}
  \qty({j}_y)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}.
\end{equation}
After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
\begin{equation} \label{eq_d14}
  \begin{aligned}
    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
    \frac{ie\hbar}{{m_e}}
    \delta_{k_x,k'_x} \\
    & \times
    \qty[
    \sqrt{\frac{n}{2}} \delta_{n',n-1}
    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
    ].
  \end{aligned}
\end{equation}

>>>>

In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system. We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(\ref{eq:1}) and we identified them as the Floquet states in Eq.~(\ref{eq:14}). For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(\ref{eq:10}) as quantum states using their corresponding quantum numbers as follows
\begin{equation} \label{eq:d1}
  \ket{\phi_{n,m}} = \ket{n,k_x}.
\end{equation}
Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
\begin{equation} \label{eq:d2}
  \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
\end{equation}
Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
\begin{equation} \label{eq:d3}
  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
\end{equation}
where $\widetilde{m}$ is the mass of the considering particle.

First, we consider the $x$-directional particle current operator component, and we can identify that as
\begin{equation} \label{eq:d4}
  \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
\end{equation}
Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
\begin{equation} \label{eq:d5}
  \left({j}_x \right)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
\end{equation}
and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq:7}) as follows
\begin{equation} \label{eq:d6}
  \begin{aligned}
    \left({j}_x \right)_{nm,n'm'} = &
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int
    \left(\hbar k'_x + eBy\right) \\
    & \times
     \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
    \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
    dy.
  \end{aligned}
\end{equation}
Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
\begin{equation} \label{eq:d7}
  \begin{aligned}
    \left({j}_x \right)_{nm,n'm'} =
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int &
    \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right] \\
    & \times
    \chi_{n}(\bar{y})
    \chi_{n'}(\bar{y})
    d\bar{y}.
  \end{aligned}
\end{equation}
Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
\begin{subequations} \label{eq:d8}
  \begin{align}
    \int
    \chi_{n}({y})
    \chi_{n'}({y}) d{y} &=
    \delta_{n',n}, \\
    \int
    y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1} \right),
  \end{align}
\end{subequations}
we simplify the matrix elements of $x$-directional current operator to obtain
\begin{equation} \label{eq:d9}
  \begin{aligned}
    &\left({j}_x \right)_{nm,n'm'} =
    \frac{eB}{{\widetilde{m}}}
    \delta_{k_x,k'_x} \\
    & \qquad\times
    \left[
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}\right)
    + \zeta(t) \delta_{n',n}
    \right].
  \end{aligned}
\end{equation}
Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
\begin{equation} \label{eq:d10}
  \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} =&
      \frac{eB}{\widetilde{m}}
      \delta_{k_x,k'_x} \\
      & \times
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1} \right).
  \end{aligned}
\end{equation}
For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
\begin{equation} \label{eq:d11}
  \begin{aligned}
      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
      \frac{e^2B}{{m_e}}
      \delta_{k_x,k'_x}\\
      & \times
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1} \right).
  \end{aligned}
\end{equation}

Moreover, we can identify the $y$-directional current operator component as
\begin{equation} \label{eq:d12}
  \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
\end{equation}
Using this operator, the matrix elements of $y$-directional current operator in Floquet mode basis can be represented as
\begin{equation} \label{eq:d13}
  \left({j}_y \right)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
\end{equation}
After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
\begin{equation} \label{eq:d14}
  \begin{aligned}
    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
    \frac{ie\hbar}{{m_e}}
    \delta_{k_x,k'_x} \\
    & \times
    \left(
    \sqrt{\frac{n}{2}} \delta_{n',n-1}
    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
    \right).
  \end{aligned}
\end{equation}
